---
title: "Filter with across"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---


Must have latest version of dplyr.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
```

## Import

```{r import}
data <- read_csv("data/data.csv")

data
```

## Variables

```{r variables}
color_values <- c("blue", "brown")
my_color_cols <- c("color_a", "color_b", "color_c")
```

## Filter with across

### Filter across to exclude rows

This is the old `filter_at` version that excludes columns where target colors exist.

```{r}
data %>% 
  filter_at(
    vars(all_of(my_color_cols)),
    all_vars(
      !(. %in% color_values)
    )
  )
```

This is the `across()` version of this:

```{r}
data %>% 
  filter(
    across(all_of(my_color_cols),
    ~ !(.x %in% color_values))
  )
```

## Filter across columns to keep rows

This used `if_any` to find rows where the color_values exist in any my_color_cols. `across()` doesn't work well with filter. [Read this](https://www.tidyverse.org/blog/2021/02/dplyr-1-0-4-if-any/).

```{r}
data %>% 
  filter(
    if_any(my_color_cols, ~ .x %in% color_values)
  )
```

## Removing columns with NA

This excludes rows when is.na is in any column. I think I need `all_of()` only if using filter? [Not quite same reference](https://dplyr.tidyverse.org/articles/colwise.html#filter).

I'm not quite sure why this doesn't work with `if_any(my_color_cols)` like above.

```{r}
data %>% 
 filter(across(all_of(my_color_cols), ~ !is.na(.x)))
```

When I first did it as `filter(across(my_color_cols, ~ !is.na(.x)))` I got this message:

Note: Using an external vector in selections is ambiguous.
ℹ Use `all_of(my_color_cols)` instead of `my_color_cols` to silence this message.
ℹ See <https://tidyselect.r-lib.org/reference/faq-external-vector.html>.










