---
title: "Across attempts"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

Must have latest version of dplyr.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
```

## Using if_any to mutate multiple columns

I want to classify rows in a new column based on any value in a list being present in any column in a list. But I want to do this using `across()` or `if_any()`.

This is what I'm looking for, listing each column in the `case_when()`. I want to replace multiple lines with one `if_any(my_color_cols)`.

```{r}
color_values <- c("blue", "brown")
color_cols <- c("hair_color", "skin_color", "eye_color")

starwars %>% 
  select(name, ends_with("color")) %>% 
  mutate(
    blue_brown = case_when(
      hair_color %in% color_values ~ TRUE,
      skin_color %in% color_values ~ TRUE,
      eye_color %in% color_values ~ TRUE,
      TRUE ~ FALSE
    )
  )
```

This is the `if_any()` rewrite of the above code.

```{r}
starwars %>% 
  select(name, ends_with("color")) %>% 
  mutate(
    blue_brown = if_any(color_cols, ~ case_when(
      .x %in% color_values ~ TRUE,
      TRUE ~ FALSE
    ))
  )
```

---

## Using smaller data set

## Import

```{r import}
data <- read_csv("data/data.csv")

data
```

## Variables

```{r variables}
my_color_cols <- c("color_a", "color_b", "color_c")
```

## Mutate with across

### case_when method for mutate

This works. It finds TRUE when either blue or brown is an any of the three columns.

```{r case-when}
data %>% 
  mutate(
    blue_red = case_when(
    color_a %in% color_values ~ TRUE,
    color_b %in% color_values ~ TRUE,
    color_c %in% color_values ~ TRUE,
    TRUE                     ~  FALSE
    )
  )
```

### if_any version of same task

This uses `if_any()` to look across my_color_cols to find any value in color_valus and mark as TRUE in a new column.


```{r}
data %>% 
  mutate(
    blue_red = if_any(all_of(my_color_cols), ~ case_when(
    .x %in% color_values ~ TRUE,
    TRUE ~  FALSE
    ))
  )
```

It seems strange to use both `if_any(all_of(my_color_rows))`, but without it I got this warning:

```text
Note: Using an external vector in selections is ambiguous.
ℹ Use `all_of(my_color_cols)` instead of `my_color_cols` to silence this message.
ℹ See <https://tidyselect.r-lib.org/reference/faq-external-vector.html>.
```

So I'll try this one more time to see if I get the same error, but using a select-type value?

```{r}
data %>% 
  mutate(
    blue_red = if_any(starts_with("color"), ~ case_when(
    .x %in% color_values ~ TRUE,
    TRUE ~  FALSE
    ))
  )
```

Yes ... perhaps the key note there is "external vector" since originally I was calling my column names from a vector created outside the data frame.

